Proposed Solution

### 2017-01-23 CAV17/secs/arch.tex

\begin{figure*}[tbp] \centering
\includegraphics[width=0.88\textwidth]{figs/overview}
\caption{\app's workflow. The green components represent configuration 
  files, including both training set of configuration files and users' input
  configuration files to verify.
  The blue dashed box is \app. 
  The yellow components are key modules of \app.
  The purple circle is a checker for checking whether the target
  configuration file violates any rule.}
\label{fig-overview}
\end{figure*}

We propose \app, an automatic verification framework for 
software configuration files.
In particular, \app can detect many sophisticated configuration errors, 
including ordering errors, missing entry errors,
type errors and integer correlation errors. 
As depicted in Figure~\ref{fig-overview}, 
a typical \app verification workflow has three steps:
translation, learning, and rule refinement. In this section, we briefly
describe how each step works.

@@

\para{Translator}
The translator module first parses the input training  
set of configuration files, and then transforms them into 
a more structured and typed intermediate representation.
When we infer the types of entries in a configuration file, 
the type of an entry cannot always be fully determined from 
a single value, since it is very hard to understand
the purposes of key-value entries in modern
software configuration files~\cite{xu15hey}.
We address this problem 
by introducing {\em probabilistic types}.
Rather than giving a variable a single type, 
we assign several types over a probability distribution. 
We can later use these more structured files
as a training set to learn the rules.

\para{Learning}
The input of the learner is a set of files that have been translated
into well-structured intermediate representations. 
The learner employs a learning algorithm named {\em rule association 
algorithm} to generate various rules,
potentially used to handle different types of configuration errors,
including ordering errors, missing entry errors,
type errors and integer correlation errors.
These rules are the outputs of the learner, 
and will be used to detect errors later.
Because the translator gives the learner probabilistically typed entries,
the learner is also responsible for determining a type for each entry.

>>>>

\begin{figure*}[tbp] \centering
\includegraphics[width=0.84\textwidth]{figs/overview}
\caption{\app's workflow. The green components represent configuration 
  files, including both training set of configuration files and users' input
  configuration files to verify.
  The blue dashed box is \app. 
  The yellow components are key modules of \app.
  The purple circle is a checker for checking whether the target
  configuration file violates any rule.}
\label{fig-overview}
\end{figure*}

We propose \app, an automatic verification framework for 
software configuration files.
As shown in Sec.~\ref{sec-motiv}, \app can detect many sophisticated 
configuration errors, including ordering errors, missing entry errors,
type errors and integer correlation errors. 
Figure~\ref{fig-overview} shows
a typical \app verification workflow with three steps:
translation, learning, and rule refinement. This section briefly
describes how each step works.

@@

\para{Translator}
The translator module first parses the input training  
set of configuration files, and then transforms them into 
a more structured and typed intermediate representation.
When we infer the types of entries in a configuration file, 
the type of an entry cannot always be fully determined from 
a single value, since it is difficult to understand
the purposes of key-value entries in modern
software configuration files~\cite{xu15hey}.
We address this problem 
by introducing {\em probabilistic types}.
Rather than giving a variable a single type, 
we assign several types over a probability distribution. 
We can later use these well-structured files
as a ``true'' training set to learn the rules.

\para{Learning}
The learner reads a set of configuration  files that have been translated
into well-structured representations. 
The learner employs a learning algorithm, {\em rule association 
algorithm}, to generate various rules,
potentially used to handle different types of configuration errors,
including ordering errors, missing entry errors,
type errors and integer correlation errors.
These rules are the outputs of the learner, 
and will be used to detect errors later.
Because the translator gives the learner probabilistically typed entries,
the learner is also responsible for determining types for these entries.

### 2017-01-23 CAV17/secs/motiv.tex

\para{Example~1: Ordering error} 
Ordering errors were reported by Yin {\em et al.}~\cite{yin11anempirical} and our first
example illustrates how ordering errors can cause a system to crash. When a user configures PHP 
to run with the
Apache HTTP Server, most likely the user will take some already existing configuration files and adapt them
to suit her needs. The configuration file might contain, among others, 
the following lines:

@@

\para{Example~3: Missing entry error} 
Many critical system outages result from the fact that an important
entry was missing from the configuration file. 
We call such a problem a {\em missing entry error}.
In a public misconfiguration dataset~\cite{configdataset},
many MySQL failure reports were caused by
missing entry errors.
Below is a real-world missing entry error example~\cite{yin11anempirical}:
when a user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
achieved via the following entries in the OpenLDAP configuration file:

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    include schema/ppolicy.schema
    overlay ppolicy
\end{lstlisting}

When using the password policy overlay in OpenLDAP, 
users must first include the related schema.
Leaving out the {\tt include schema/ppolicy.schema} entry, 
as done by many users~\cite{yin11anempirical}, 
causes the failure of LDAP. 
If the user runs \app on such a misconfiguration file,
\app would return:

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    MISSING ENTRY ERROR: Expected "overlay" "ppolicy"
    in the same file: "include" "schema/ppolicy.schema"
\end{lstlisting}

\para{Example~4: Type errors} 
Many system availability problems are caused by 
assigning incorrect type of values to some key in configuration
files. Consider the following real-world misconfiguration
file~\cite{typeerror}: 
a user tries to install MySQL and she needs to initiate the path
of the log information generated by MySQL.
This user puts the following entry assignment in her MySQL
configuration file:

@@

>>>>

\para{Example~1: Missing entry error} 
Many critical system outages result from the fact that an important
entry was missing from the configuration file. 
We call such a problem a {\em missing entry error}.
In a public misconfiguration dataset~\cite{configdataset},
many misconfiguration issues were caused by
missing entry errors.
Below is a real-world missing entry error example~\cite{missingentry}:
when a user wants to configure her PHP and PostgreSQL,
she needs to use both {\tt pgsql.so} and {\tt curl.so}
in her {\tt /ctc/php5/conf.d/curl.ini} file.
Specifically, this is usually
achieved by the following entries in 
the curl configuration file:

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    extension=pgsql.so
    extension=curl.so
\end{lstlisting}

Nevertheless, in this example, the user 
left out the {\tt extension=pgsql.so} entry, 
as done by many users~\cite{yin11anempirical, missingentry}, 
causing a segmentation fault. 
If the user runs \app on such a misconfiguration file,
\app would return:

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    MISSING ENTRY ERROR: Expected "extension=pgsal.so"
    in the same file: "extension=curl.so"
\end{lstlisting}

@@

\para{Example~3: Type errors} 
Many system availability problems are caused by 
assigning incorrect type of values to some key in configuration
files. Consider the following real-world misconfiguration
file~\cite{typeerror}: 
a user tries to install MySQL and she needs to initiate the path
of the log information generated by MySQL.
This user puts the following entry assignment in her MySQL
configuration file:

@@

\para{Example~4: Ordering error} 
Ordering errors were reported by Yin {\em et al.}~\cite{yin11anempirical} and our first
example illustrates how ordering errors can cause a system to crash. When a user configures PHP 
to run with the
Apache HTTP Server, most likely the user will take some already existing configuration files and adapt them
to suit her needs. The configuration file might contain, among others, 
the following lines:
